How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-06-10 Draft_June_2022/Full_draft_20220608.rmd
forget cached

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(ggplot2)
library(tidyr)
library(skimr)
library(scales)
library(RColorBrewer)
library(nnet)
library(stargazer)
library(kableExtra)
library(tm)
library(tidytext)
library(topicmodels)
library(tibble)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

@@

model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
                  data = ama_model, model = TRUE, trace = FALSE)

@@

p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
# Independence of Irrelevant Alternatives (Hausman-McFadden) test, in practice
iia_data <- filter(ama_model, mx_cat != "Pure Economic Integration")
iia <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
                data = iia_data, model = TRUE, trace = FALSE)
iia_summary <- summary(iia)
iia_p_values <- round((1 - pnorm(abs(summary(iia)$coefficients/summary(iia)$standard.errors)))*2, 5)
# Model coefficients, and p-values, are statistically identical even when we drop the largest
# factor category from model. Therefore, we can proceed with a multinomial logit model,
# instead of a multinomial probit model, since the independence of irrelevant alternatives 
# Other post estimation tests
chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
# Chi-square p value (p-value < 0.001) tells us that our model explains a
# significant amount of the variation in the data in comparison with a null model.
# But too much information on the summary tables... Let's just focus on what we want here:
logit2prob <- function(logit) {
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
} # to transform log odds in probabilities

>>>>

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(ggplot2)
library(tidyr)
library(skimr)
library(scales)
library(RColorBrewer)
library(nnet)
library(stargazer)
library(kableExtra)
library(tm)
library(tidytext)
library(topicmodels)
library(tibble)
library(readxl)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

         env_vs_all <- ifelse(mx_cat == "Pure Conservation", 1, 0),

@@

model <- glm(env_vs_all ~ km_to_manaus + election_year + def_year + AAI,
             family = binomial(link = 'logit'), data = ama_model)

@@
